Advisors and Mentors are some of the most important people any scientist (or
human being) can encounter. Time and again, I have heard colleagues speak of
"that one inspirational" person that drove them to be their best, helped them
grow personally and professionally, and refused to give up on them even when
doing so might even be the `correct' course of action.

I am very lucky in that I suffer from an embarassment of riches in this regard.
The path I've trodden over the course of my life, academic career, and
transition to a professional career has been litered with people who have
uplifted, supported, and educated me. For that, I am profoundly grateful, and
owe a debt that can truly only be paid by mentoring, supporting, and uplifting
others.

I am indebted to my advisor, Ken Barish, whose calm, stoic and unabated support
helped guide me through my research. Ken involved me in many aspects of the
research group at UCR, beyond the scientific work. He insured that I was
exposed to all aspects of research in particle physics, including writing
grants, reviewing literature, mentoring younger students, building detectors,
running a research group.  Ken has always had the uncanny ability to know who
to talk to, and has used that ability to connect me with other excellent
physicists, who in turn helped me grow as a researcher. Ken's style of advising
gave me the freedom I needed to pursue my interests, and move in the scientific
directions I felt most fruitful, while still helping to provide provide an
overall direction for my academic career and research. 

Thought maybe it sounds a bit silly, I am most personally grateful to Ken for
when he gave me a second chance in graduate school. I suspect he did not
realize how close I was to being unable to continue on in graduate school when
he admitted me to his group.

When Ken accepted me into his group, I was an undoubtedly risky choice. I
struggled mightily my first year in grad school.  I earned poor grades and had
effectively failed the first course in Electricity and Magnetism. In fact, my
performance was so poor, that the administration reduced my teaching privilags
to give me more time to focus on academics. I had no income for the summer,
since my grades did not entitle me to continue to receive financial support
from the graduate division fellowship.

In fact, I was not even admitted to graduate school to study high-energy physics
- I was admitted for condensed matter physics. However, I was interested in the
research carried out by Ken and Rich Seto's heavy ion group, so I talked to Ken,
who graciously accepted me into the group, provided me with academic and
financial support. He even flew me out to Brookhaven National Lab my first
summer of graduate school. I finally got to dive into `real' physics research.
I think it was this vote of confidence from Ken, as well as the awesome physics
happening at the PHENIX experiment which gave me the confidence to
wholeheartedly devote myself to my studies and research.  My grades improved,
and I gained the confidence I needed to succeed in graduate school.  Without
Ken's intervention, I fear that my graduate career would have been over in short
order.

While at Brookhaven National Lab, I encountered graduate students, post docs,
research staff, and other amazing physicists who taught me an incredible
amount. I was met with patience, kindess, friendship and mentorship.

Richard Hollis was one of the first people I encoutered in my research group at
UCR--I have never met a more patient person. Richard helped me get my bearings,
and set me straight, during my early (and later) years of graduate school. Even
after Richard left our group for other opportunities elsewhere, he provided me
with invaluable feedback on this document.  

I encountered K. Oleg Eyser during my early years with the UCR group as well. I
recall that he was less than thrilled to have yet another ``green'' graduate
student constantly asking questions. Dispite his sizable workload, he still made
time to teach me, and introduced me to the very complicated PHENIX software
system.  Oleg challenged me to find answers for myself, and was unrelenting in
that regard. I am certain that this made me a better researcher.

A graduate student I met during my first shift (simultaneous data acquisition
and high voltage monitoring), Josh Perry, gave me a crash course on the PHENIX
operations, boiling down this incredibly complicated system into understandable
pieces. He helped me learn that ultimately, persistance pays off when tackling
difficult problems.  

Martin Leitgab took me under his wing while I worked days and nights to learn
PHENIX's fast data production systems.  Martin's systematic, calm, and patient
approach to problem solving has been something I have tried to emulate since my
work with him--I could not have asked for a better mentor for that project. 

On that same project was my first introduction to Chris Pinkenburg and Martin
Purschke--somewhat of the yin and yang of the PHENIX online data aquisition. I
benefited enormously from conversations with both regarding PHENIX software,
and online systems. Martin Purschke's kindness and sense of humor always
spurred me on, while Chris' dogged dedication to doing things `the right way'
kept me honest. I have returned to Martin and Chris with various questions many
times over the years, and have always benefitted from their wisdom.

Likely no one has been woken up so many times with emergencies at the PHENIX
counting house in the middle of the night then Martin, yet even when I woke him
at 3 am on many occasions, would simply state, in an execptionally dry, well
practiced line: ``Martin Speaking, please state the nature of your emergency''. I
don't know of many who can manage to be coy and good natured under such
circumstances. I recall on another occasion, I was the one recieving a late
night call--and I did my best to channel Martin when I was greeted from the
PHENIX counting house with: ``Mike, what the hell is wrong with the spin
montor!?''.

I have to acknoledge Joe Seele as well, in this regard, as he probably more
than anyone else, set me on the path to learning to program well, and using a
computer effectively--these skills, so often neglected in Particle Physics,
have paid off for me, many, many times over.

There is no way that I would have grown as much as I did in my later years in
grad school, had I not had the fabulous opportunity to work with Dr. Ralf
Seidl, Dr. Francesca Giordano, and Daniel Jumper. Francesca tutored me in the
ways of hardware assembly--it was quite a proud moment for me to see the
detectors that I put together with my own hands, mounted on the front of the
PHENIX muon tracker nose cone. Francesca knocked it out of the park with her
leaderhship in the RPC program. She has this ineffable dogged determination,
and ability to break down problems into manageable pieces--a quality I have
done my best to emulate, and see in nearly all physicsists that I respect.

I owe Ralf a huge debt for his persistance and leadership in the W-Analysis,
which to date has resulted in six different thesis analyses. Ralf has always
demonstrated a willingness to walk students through a tough problem, and an
admirable hard-headedness when it comes to dealing without people that maybe
need to put in a bit more effort in their research and work. Though I have at
times been on the recieving end of this, the result has always been a very
strong motivation to do right by him, and pick up my slack.

Daniel has been an absolute lifesaver, and a dear friend. He and I have worked
essentially in concert on the W-Analysis, and our frequent collaboration over
skype, in person, and around the world has really helped keep my direction in
the analysis straight and true.  We often traded the latest VIM secrets, and
carefully cross-checked eachothers' work. It is rare to have a colleauge like
Daniel backing you up, and I'm very thankful for the opportunity to work with
him.

I am also greatful for the rest of the W-Analysis team, Dr. Abraham Meles, Dr.
Sangwha Park and Dr. Chong Kim. Everyone has doggedly stuck together for many
cross-checks, and when our analysis is finally published, the collective hard
work of Ralf, Francesca, Sanghwa, Chong and Abraham will shine through.

In fact, I owe the entire W-Analysis team, consisting of Ralf, Chong,
Francesca, Daniel, Sanghwa, Abraham, and Richard Hollis a huge debt of
gratitude. The work in this thesis has largely been carried out in close
collaboration with this fantastic team--especially with regards to Chapters 5,
6 and 7.

Additionally, I must acknoledge Dr. Ciprean Gal and Dr. Hideyuki Oide, who both
wrote excellent theoretical introductions to their respective theses, which I
have relied upon to help guide my own, in Chapter 3.

Angelika Drees and Amaresh Datta were both very helpful to me in directing and
discussing my progress with the `Vernier Analysis'.

I must also acknowlege my dear friends I've made through traversing the graduate
school program at UCR. In particular, my dear and life-long friends I've made as
part of living in the ``FZX House'' for the last seven years--Chris Heidt, Behnam
Darvish Sarvestani, Pat Odenthal, Oleg Martynov, and Corey Kownacki. You guys
are my second family, and without your friendship, I would not be the man I am
today.

Additionally, I must also acknowledge my dear friends Alex Natale and Jackie
Hubbad--my `gym squad'. Without their constant companionship at the gym, I
surely would be obese and depressed after such a long haul in grad school.

I've been the beneficiary of tremendous support from my mother and father, Bob
and Marian, and my two brothers, Joe and David, and my girlfriend, Emily.
I'm sure you all have been on the receving end of an uncountable number of
miseries inflicted by my stressed-self during the rigors of graduate school, yet
you've all stuck with me, and loved me.  Thank you.

Finally, there are many that have gone unacknowledged by name--other dear
friends, teachers, mentors. It is impossible to think of all the ways that the
various people I've encountered in my life have helped grow me. It is to the
singular idea of this, that I dedicate my thesis.
